Visualizing anesthesia-induced vasodilation of cerebral vasculature using multi-exposure speckle imaging

### 2020-06-10 article.tex
Added funding sources
Remove C. X. as author

\author[a]{Colin T. Sullender}
\author[a]{Lisa M. Richards}
\author[b]{Fei He}
\author[b,c]{Chong Xie}
\author[b,c]{Lan Luan}
\author[a,*]{Andrew K. Dunn}
\affil[a]{Department of Biomedical Engineering, University of Texas at Austin, 107 W. Dean Keeton Street Stop C0800, Austin, Texas, 78712, United States}
\affil[b]{Department of Electrical and Computer Engineering, Rice University, 6100 Main Street, Houston, TX, 77005, United States}
\affil[c]{Department of Bioengineering, Rice University, 6100 Main Street, Houston, TX, 77005, United States}

@@

\subsection*{Author Contributions}
C.T.S. and L.M.R. constructed the imaging system, conceived the experiments, and acquired the data. C.T.S analyzed the results and wrote the manuscript. F.H. performed the animal surgeries. C.X., L.L., and A.K.D. supervised the project. All authors contributed to the manuscript revisions.

\acknowledgments
This study was supported by the National Institutes of Health...

@@

\vspace{2ex}\noindent\textbf{Chong Xie} is an Associate Professor in the Department of Electrical and Computer Engineering at Rice University and a member of the Rice Neuroengineering Initiative. His research focuses on the development of advanced nanoelectronic devices for probing and manipulating neural systems.

>>>>

\author[a]{Colin T. Sullender}
\author[a]{Lisa M. Richards}
\author[b]{Fei He}
\author[b,c]{Lan Luan}
\author[a,*]{Andrew K. Dunn}
\affil[a]{Department of Biomedical Engineering, University of Texas at Austin, 107 W. Dean Keeton Street Stop C0800, Austin, Texas, 78712, United States}
\affil[b]{Department of Electrical and Computer Engineering, Rice University, 6100 Main Street, Houston, TX, 77005, United States}
\affil[c]{Department of Bioengineering, Rice University, 6100 Main Street, Houston, TX, 77005, United States}

@@

\subsection*{Author Contributions}
C.T.S. and L.M.R. constructed the imaging system, conceived the experiments, and acquired the data. C.T.S analyzed the results and wrote the manuscript. F.H. performed the animal surgeries. L.L. and A.K.D. supervised the project. All authors contributed to the manuscript revisions.

\acknowledgments
This study was supported by the National Institutes of Health (Nos. EB011556 and NS108484).

@@
